Zambia Potential Yield Grids

### 2016-01-21 Rmd/all-inputs.Rmd
Temporary fix for low-biased soybean yield with FAO GAEZ yields (bias-correction). In maize-soy-grid.Rmd. Processed resulting surfaces in all-inputs.Rmd to data.table inputs

p_proj <- "/Users/lestes/Dropbox/publications/zambiaToff/private/zambiaToff/"
p_devel <- full_path(p_proj, "external/input_devel/cropland")
p_basedat <- paste0("/Users/lestes/Dropbox/projects/agroEcoTradeoff/external/",
                    "base_data/")
p_crop <- full_path(p_proj, "external/input_devel/cropland")
p_bd <- full_path(p_proj, "external/input_devel/biodiversity")
p_cost <- full_path(p_proj, "external/input_devel/roads/cost")

# Load in data
mgrid <- raster(full_path(p_basedat, "ZA-grid.tif"))
cropland <- raster(full_path(p_crop, fname = "cropland-1k.tif"))
bd <- raster(full_path(p_bd, fname = "bdprior.tif"))
vegr <- raster(full_path(p_bd, fname = "ZA-vegremain.tif"))
cost <- raster(full_path(p_cost, fname = "zamcost.tif"))

@@

>>>>

p_proj <- "/Users/lestes/Dropbox/publications/zambiaToff/private/zambiaToff/"
p_devel <- full_path(p_proj, "external/input_devel/cropland")
p_basedat <- paste0("/Users/lestes/Dropbox/projects/agroEcoTradeoff/external/",
                    "base_data/")
p_crop <- full_path(p_proj, "external/input_devel/cropland")
p_bd <- full_path(p_proj, "external/input_devel/biodiversity")
p_cost <- full_path(p_proj, "external/input_devel/roads/cost")
p_yield <- full_path(p_proj, "external/input_devel/yield")
p_h20 <- full_path(p_proj, "external/input_devel/water")
p_terr <- full_path(p_proj, "external/input_devel/terrain")
p_carb <- full_path(p_proj, "external/input_devel/carbon")
p_production <- full_path(p_proj, "external/data/production")

# Load in data
mgrid <- raster(full_path(p_basedat, "ZA-grid.tif"))
cropland <- raster(full_path(p_crop, fname = "cropland-1k.tif"))
bd <- raster(full_path(p_bd, fname = "bdprior.tif"))
vegr <- brick(full_path(p_bd, fname = "ZA-vegremain.tif"))
load(full_path(p_bd, fname = "ZA-vegremain.rda"))
names(vegr) <- vegnames
carbon <- brick(full_path(p_carb, fname = "ZA-carbon.tif"))
names(carbon) <- c("veg", "soil")
cost <- raster(full_path(p_cost, fname = "ZA-cost.tif"))
ynms <- dir(p_yield, pattern = "tif")
ynms <- sapply(c("S", "R", "I"), function(x) ynms[grep(x, ynms)])
ynms <- ynms[c(1, 3, 5, 2, 4, 6)]
ylds <- lapply(ynms, function(x) {
  b <- brick(full_path(p_yield, x))
  ylnms <- gsub("\\.tif", "\\.rda", x)
  load(full_path(p_yield, ylnms))
  names(b) <- layernms
  b
})
names(ylds) <- gsub("_10K", "", ynms)

# mask materials
remfrac <- raster(full_path(p_bd, fname = "ZA-remfrac.tif"))
water <- raster(full_path(p_h20, fname = "water-1k.tif"))
farmable <- raster(full_path(p_terr, fname = "farmable-1k.tif"))

@@

## Create farmable area

```{r, eval=FALSE}
# merge together the three farmland available masks
avail <- remfrac - water
avail[avail < 0] <- 0
avail <- avail - (1 - farmable)
avail[avail < 0] <- 0
avail <- avail * (bd < 0.962)  # remove PAs entirely (1 if nps, 0.962 if GMAs)
# plot(avail)
```

That creates the farmland availability mask that is needed.

## Stack and mask all grids
```{r, eval = FALSE}

# first get rid of all NA area in all grids
# start with yield grids
yldmask <- calc(stack(ylds), sum)
yldmask2 <- disaggregate(yldmask, fact = 10)
yldmask3 <- resample(yldmask, yldmask2)
yldmask4 <- projectRaster(yldmask3, mgrid)
yldmask5 <- mask(yldmask4, mgrid)
plot(yldmask5)

# now with other
carbonf <- stack(lapply(1:nlayers(carbon), function(x) {
  r <- carbon[[x]]
  r[is.na(r)] <- 0
  r
}))

mgridc <- crop(mgrid, avail)
inlist <- list("convertible" = avail, "vegremain" = vegr, "carbon" = carbonf, 
               "cost" = cost, "bd" = bd, "cropland" = cropland)
inlist <- lapply(inlist, function(x) crop(x, mgridc))
inlist2 <- lapply(inlist, function(x) calc(x, mean))
inlist3 <- calc(stack(inlist2), mean)

# filter NA values
nafilt <- calc(stack(!is.na(inlist3), !is.na(crop(yldmask5, mgridc))), sum)
# plot(nafilt)
# plot(!is.na(calc(vegr, mean)))
# plot(!is.na(crop(yldmask5, mgridc)), col = c("transparent", "red"), add = TRUE)
msk <- nafilt == maxValue(nafilt)
msk[msk == 0] <- NA

# updated mask
mgridf <- mask(mgridc, msk)
valinds <- which(!is.na(values(mgridf)))
outlist <- inlist[names(inlist) != "cropland"]

# write out new data.tables
cnames <- "ZA"  
onms <- names(inlist)
onms[onms == "bd"] <- "cons-priorities"
for(i in 1:length(outlist)) { # i <- 1
  fnm <- full_path(p_production, paste0(cnames, "-", onms[i], ".csv"))
  DT <- as.data.table(outlist[[i]], xy = FALSE)[valinds, ]
  write.table(DT, file = fnm, sep = ",", col.names = TRUE, row.names = FALSE)
}

# write out mask raster
base <- as.data.table(msk, xy = TRUE)
setnames(base, old = names(msk), new = "val")
base[, ind := 1:nrow(base)]
base <- base[!is.na(val)][, val := NULL]
fnm <- full_path(p_production, paste0(cnames, "-mask.csv"))
write.table(base, file = fnm, sep = ",", col.names = TRUE, row.names = FALSE)
# plot(dt_to_raster(base, mgridf@crs))

## Yield grids
```{r, eval = FALSE}
# Function to disaggregate and reproject yield rasters
yld_disagg <- function(x, msk, fact = 10) {
  r <- disaggregate(x, fact = 10)
  r2 <- resample(x, r)
  r3 <- projectRaster(r2, msk)
  r4 <- mask(r3, msk)
  r4
}

# Function to aggregate yields within a particular yield brick
# stat <- "50"; cults <- paste0("9900", c("08", "09", "10"))
yield_stat <- function(x, stat = "mu", mgmnt = "S", cults, fun = mean) {
  repstr <- paste0(paste0(stat, "_", mgmnt), cults, collapse = "|")
  cnms <- names(x)[grep(repstr, names(x))]
  print(cnms)
  calc(x[[cnms]], fun = fun)
}
# rm(stat, mgmnt, cults, fun, x, cnms, repstr)

# Let's make an initial yield combination for model development that is
# is composed of: 
# maize
# 1. Subsistence management, all four cultivars, median yields, 50%
# 2. Rainfed commerical, hybrid cultivars, median yields, 40%
# 3. Irrigated maize, hybrid cultivars, median yields, 10%

maize <- list("S" = yield_stat(x = ylds$maize_S.tif, "50", "S", 
                               paste0("000", 1:4)), 
              "R" = yield_stat(x = ylds$maize_R.tif, "50", "R", 
                               paste0("000", 3:4)), 
              "I" = yield_stat(x = ylds$maize_I.tif, "50", "I", 
                               paste0("000", 3:4)))
wgts <- c(0.5, 0.4, 0.1)
maizewgt <- lapply(1:length(wgts), function(x) maize[[x]] * wgts[x])
potmaize <- calc(stack(maizewgt), sum)  # potential maize yield

# Soybean
# 1. Subsistence management, all 3 cultivars, median yields, 20%
# 2. Rainfed commerical, all 3cultivars, median yields, 70%
# 3. Irrigated maize, all 3 cultivars, median yields, 10%
soy <- list("S" = yield_stat(x = ylds$soybean_S.tif, "50", "S", 
                             paste0("9900", c("08", "09", "10"))), 
            "R" = yield_stat(x = ylds$soybean_R.tif, "50", "R", 
                             paste0("9900", c("08", "09", "10"))), 
            "I" = yield_stat(x = ylds$soybean_I.tif, "50", "I", 
                             paste0("9900", c("08", "09", "10"))))
wgts <- c(0.2, 0.7, 0.1)
soywgt <- lapply(1:length(wgts), function(x) soy[[x]] * wgts[x])
potsoy <- calc(stack(soywgt), sum)  # potential maize yield
# plot(potmaize); cellStats(potmaize, mean)
# plot(potsoy); cellStats(potsoy, mean)
# plot(potmaize)
# plot(potsoy)

# Disaggregate potential yields, stack, and round
ylds_1k <- lapply(list(potmaize, potsoy), function(x) {
  yld_disagg(x, msk = mgridf)
})
ylds_s <- stack(ylds_1k) 
names(ylds_s) <- c("maize", "soy")
ylds_s <- round(ylds_s)

# data.table them
cnames <- "ZA"  
fnm <- full_path(p_production, paste0(cnames, "-potential-yields.csv"))
DT <- as.data.table(ylds_s, xy = FALSE)[valinds, ]
write.table(DT, file = fnm, sep = ",", col.names = TRUE, row.names = FALSE)

### 2016-01-21 Rmd/biodiversity-layer.Rmd
Temporary fix for low-biased soybean yield with FAO GAEZ yields (bias-correction). In maize-soy-grid.Rmd. Processed resulting surfaces in all-inputs.Rmd to data.table inputs

# keep for assessing impacts
writeRaster(sm, filename = full_path(p_bd, "ZA-vegremain.tif"), 
            overwrite = TRUE)

>>>>

# keep for assessing impacts
writeRaster(sm, filename = full_path(p_bd, "ZA-vegremain.tif"), 
            overwrite = TRUE)
vegnames <- gsub("\\.tif", "", gsub("veg", "v", vnms))
save(vegnames, file = full_path(p_bd, "ZA-vegremain.rda"))

### 2016-01-21 Rmd/cropland.Rmd
Temporary fix for low-biased soybean yield with FAO GAEZ yields (bias-correction). In maize-soy-grid.Rmd. Processed resulting surfaces in all-inputs.Rmd to data.table inputs

# corresponding FAOStat full country values are 1211566 and 3020380 for maize
# 56839 and 116539 for soybean
nwrepl <- fao[Crop == "Maize" & var == "prod" & Year == "2008" & 
                provcode != 3431, 1211566 - sum(Value)]
fao[Crop == "Maize" & var == "prod" & Year == "2008" & 
                provcode == 3431, Value := nwrepl]
srepl <- fao[Crop == "Maize" & var == "prod" & Year == "2011" & 
               provcode != 3433, 3020380 - sum(Value)]
fao[Crop == "Maize" & var == "prod" & Year == "2011" & 
                provcode == 3433, Value := srepl]
nwrepl <- fao[Crop == "Soybeans" & var == "prod" & Year == "2008" & 
                provcode != 3431, 56839 - sum(Value)]
fao[Crop == "Soybeans" & var == "prod" & Year == "2008" & 
                provcode == 3431, Value := nwrepl]
srepl <- fao[Crop == "Soybeans" & var == "prod" & Year == "2011" & 
               provcode != 3433, 116539 - sum(Value)]
fao[Crop == "Soybeans" & var == "prod" & Year == "2011" & 
                provcode == 3433, Value := srepl]

# Planted area and production 2010-2014 for Zambia
muprod <- lapply(c("Maize", "Soybeans"), function(x) {
  fao[Crop == x & var == "prod" & Year %in% c(2008:2015), sum(Value), 
      by = Year]
})
names(muprod) <- c("maize", "soy")
mupa <- lapply(c("Maize", "Soybeans"), function(x) {
  fao[Crop == x & var == "pa" & Year %in% c(2008:2015), sum(Value), 
      by = Year]
})
names(mupa) <- c("maize", "soy")

# Read in USDA harvested area and production to get difference in harvested area
# and planted area
fnms <- dir(p_usda, full.names = TRUE)
vars <- c("maize", "soy")
usda <- rbindlist(lapply(1:length(fnms), function(x){
  DT <- fread(fnms[x], stringsAsFactors = FALSE, header = TRUE)
  # cbind(vars[x], DT)
}))
cols <- names(usda)[4:9]
usda_ylds <- usda[var == "prod", cols, with = FALSE] / 
  usda[var == "harvarea", cols, with = FALSE]

>>>>

# corresponding FAOStat full country values are 1211566 and 3020380 for maize
# 56839 and 116539 for soybean
nwrepl <- fao[Crop == "Maize" & var == "prod" & Year == "2008" & 
                provcode != 3431, 1211566 - sum(Value)]
fao[Crop == "Maize" & var == "prod" & Year == "2008" & 
                provcode == 3431, Value := nwrepl]
srepl <- fao[Crop == "Maize" & var == "prod" & Year == "2011" & 
               provcode != 3433, 3020380 - sum(Value)]
fao[Crop == "Maize" & var == "prod" & Year == "2011" & 
                provcode == 3433, Value := srepl]
nwrepl <- fao[Crop == "Soybeans" & var == "prod" & Year == "2008" & 
                provcode != 3431, 56839 - sum(Value)]
fao[Crop == "Soybeans" & var == "prod" & Year == "2008" & 
                provcode == 3431, Value := nwrepl]
srepl <- fao[Crop == "Soybeans" & var == "prod" & Year == "2011" & 
               provcode != 3433, 116539 - sum(Value)]
fao[Crop == "Soybeans" & var == "prod" & Year == "2011" & 
                provcode == 3433, Value := srepl]
save(fao, file = full_path(p_devel, "fao-yields.rda"))

# Planted area and production 2010-2014 for Zambia
muprod <- lapply(c("Maize", "Soybeans"), function(x) {
  fao[Crop == x & var == "prod" & Year %in% c(2008:2015), sum(Value), 
      by = Year]
})
names(muprod) <- c("maize", "soy")
mupa <- lapply(c("Maize", "Soybeans"), function(x) {
  fao[Crop == x & var == "pa" & Year %in% c(2008:2015), sum(Value), 
      by = Year]
})
names(mupa) <- c("maize", "soy")
# mean(muprod$soy[, V1] / mupa$soy[, V1])

# Read in USDA harvested area and production to get difference in harvested area
# and planted area
fnms <- dir(p_usda, full.names = TRUE)
vars <- c("maize", "soy")
usda <- rbindlist(lapply(1:length(fnms), function(x){
  DT <- fread(fnms[x], stringsAsFactors = FALSE, header = TRUE)
  # cbind(vars[x], DT)
}))
cols <- names(usda)[4:9]
usda_ylds <- usda[var == "prod", cols, with = FALSE] / 
  usda[var == "harvarea", cols, with = FALSE]
save(usda, file = full_path(p_devel, "usda-yields.rda"))

### 2016-01-21 Rmd/maize-soy-grid.Rmd
Temporary fix for low-biased soybean yield with FAO GAEZ yields (bias-correction). In maize-soy-grid.Rmd. Processed resulting surfaces in all-inputs.Rmd to data.table inputs

p_root <- lmisc::set_base_path()
p_crop <- "~/Dropbox/data/agricultural/zambia/dssat/"
p_cropmod <- "~/Dropbox/projects/rCropMod/external/ext_data/"
p_agro <- "~/Dropbox/projects/agroEcoTradeoff/external/base_data/"
p_yield <- full_path(p_root, "external/input_devel/yield")

@@

    # unique(ID$WTH)[!unique(ID$WTH) %in% unique(substr(cr$WTH, 1, 4))]

    # cr[, .N, by = .(TNAM, SOL, Zone)][which(N > 62), ]
    # tst <- cr[TNAM == "AAAX0003" & SOL == "WI_FLSO001", ][order(YR), ]
    # plot(tst[YR > 31, HWAH], tst[YR <= 31, HWAH])
    # cr[TNAM == "AAEA0001" & SOL == "WI_CMZR003", ]

@@

    # anncv <- solmu[, round(cv(V1)), by = .(WTH, Zone)][, V1]
    # setnames(anncv, "V1", "acv")

    # annwv2[WTH == "AERM" & Zone == "Zone3",]
    # crm[WTH == "AERM" & Zone == "Zone3" & YR == 1, 
    # weighted.var2(HWAH, SharePct)]
    # annwv2[, sqrt(V1)] / solmu[, V1]  # checks

    # CV due to soil
    annmu <- crm[, round(mean(HWAH)), by = .(WTH, SOL, Zone, SharePct)]
    # cr[, .N, by = .(TNAM, SOL)][which(N > 62), ]
    # crm[WTH == "AAAI" & SOL == "WI_LVUY032" & Zone == "Zone2a", ]
    # crm[WTH == "AAAI" & SOL == "WI_LVUY032" & Zone == "Zone3", mean(HWAH)]
    # annmu[WTH == "AAAI" & Zone == "Zone3", ]
    # crm[WTH == "AAAI" & Zone == "Zone3" & SOL == "WI_LVUY032", mean(HWAH)]
    # range(crm[, round(mean(HWAH)), by = .(WTH, SOL, Zone)][, V1] - 
    # crm[, round(mean(HWAH)), by = .(WTH, SOL, Zone, SharePct)][, V1])
    # crm[WTH == "AAAA" & Zone == "Zone3" & SOL == "WI_CLBW256", mean(HWAH)]
    # annmu[WTH == "AAAA" & Zone == "Zone3" & SOL == "WI_CLBW256", ]
    annsolmu <- annmu[, weighted.mean(V1, SharePct), by = .(WTH, Zone)]
    # sum(annsolmu$V1 - annmu[, weighted.mean(V1, SharePct), 
    # by = .(WTH, Zone, SOL)][, V1])
    solcv <- annmu[, sqrt(weighted.var(V1, w = SharePct, na.rm = TRUE)), 
                   by = .(WTH, Zone)][, V1 / annsolmu[, V1] * 100]
    scvnm <- paste0("scv", snm)
    annsolmu[, c(scvnm) := round(solcv)]
    annsolmu[, V1 := NULL]
    setkeyv(annsolmu, c("WTH", "Zone"))
    idt <- idt[annsolmu]
    setkeyv(idt, c("WTH", "Zone"))
    idt
  }
  idt
})
names(cv_rasts) <- crops

@@

# ra
yld_rl <- lapply(crops, function(x) {  # x <- crops[[1]]
  yr <- lapply(c("S", "R", "I"), function(y) {  #y <- "S"
    ylds <- yld_rasts[[x]]
    nms <- names(ylds)
    cnms <- nms[grep(paste0("y.*._", y), nms)]
    r <- dt_to_raster(ylds[, c("x", "y", cnms), with = FALSE], CRSobj = gcs)
    w <- matrix(ncol = 3, nrow = 3, rep(1, 9))
    rfoc <- sapply(1:nlayers(r), function(i) rfoc <- yield_fix(r[[i]], w = w))
    names(rfoc) <- names(r)
    rs <- stack(rfoc)
    rs
  })
  named_out(yr, c("S", "R", "I"))
})
names(yld_rl) <- crops

for(i in 1:length(yld_rl)) {
  rl <- yld_rl[[i]]
  for(j in 1:length(rl)) {
    fnm <- full_path(p_yield, paste0(crops[i], "_", names(rl)[j], "_10K.tif"))
    writeRaster(rl[[j]], filename = fnm)
  }
}
```
<a href="#top">Back to top</a>

@@

This provides the methods for taking 10 km grids, averaging them across cultivars within management treatments, and then reseampling to 1 km grids. This is approximately the approach that will be used to make inputs for the tradeoff model. Other methods to explore include blending different types of management practice, e.g. X% of each cell is irrigated, Y% is rainfed commercial, Z% is subsistence. 
```{r, eval=FALSE}
yld_mus <- lapply(crops, function(x) {  # x <- crops[[1]]
  ymu <- lapply(c("S", "R", "I"), function(y) {  #y <- "S"
    cnms <- names(yld_rasts[[x]])[grep(paste0("mu_", y), names(yld_rasts[[x]]))]
    ylds <- copy(yld_rasts[[x]][, c("x", "y", cnms), with = FALSE])
    ylds[, c(x) := round(rowMeans(.SD)), .SDcols = cnms]
    ylds[, c(cnms) := NULL]
    ylds
  })
  named_out(ymu, c("S", "R", "I"))
})
names(yld_mus) <- crops
plot(dt_to_raster(yld_mus[[2]]$R, CRSobj = gcs))

>>>>

p_root <- lmisc::set_base_path()
p_crop <- "~/Dropbox/data/agricultural/zambia/dssat/"
p_cropmod <- "~/Dropbox/projects/rCropMod/external/ext_data/"
p_agro <- "~/Dropbox/projects/agroEcoTradeoff/external/base_data/"
p_yield <- full_path(p_root, "external/input_devel/yield")
p_cropland <- full_path(p_root, "external/input_devel/cropland")
p_fao <- "~/Dropbox/data/agricultural/fao/aez/soybean/"

@@

@@

    # CV due to soil
    annmu <- crm[, round(mean(HWAH)), by = .(WTH, SOL, Zone, SharePct)]
    annsolmu <- annmu[, weighted.mean(V1, SharePct), by = .(WTH, Zone)]
    solcv <- annmu[, sqrt(weighted.var(V1, w = SharePct, na.rm = TRUE)), 
                   by = .(WTH, Zone)][, V1 / annsolmu[, V1] * 100]
    scvnm <- paste0("scv", snm)
    annsolmu[, c(scvnm) := round(solcv)]
    annsolmu[, V1 := NULL]
    setkeyv(annsolmu, c("WTH", "Zone"))
    idt <- idt[annsolmu]
    setkeyv(idt, c("WTH", "Zone"))
    idt
  }
  idt
})
names(cv_rasts) <- crops

@@

# ra
w <- matrix(ncol = 3, nrow = 3, rep(1, 9))
yld_rl <- lapply(crops, function(x) {  # x <- crops[[1]]
  yr <- lapply(c("S", "R", "I"), function(y) {  # y <- "S"
    ylds <- yld_rasts[[x]]
    nms <- names(ylds)
    cnms <- nms[grep(paste0("y.*._", y), nms)]
    r <- dt_to_raster(ylds[, c("x", "y", cnms), with = FALSE], CRSobj = gcs)
    rfoc <- sapply(1:nlayers(r), function(i) rfoc <- yield_fix(r[[i]], w = w))
    names(rfoc) <- names(r)
    rs <- stack(rfoc)
    rs
  })
  named_out(yr, c("S", "R", "I"))
})
names(yld_rl) <- crops

```

## Short-term soybean fix

Potential soybean yields are too low for Zambia, so we will adjust them up with FAO-GAEZ yields

```{r, eval = FALSE}
faonms <- dir(p_fao, full.names = TRUE)
file.rename(faonms, gsub("res02crav6190|yld_package", "", faonms))
faonms <- dir(p_fao, full.names = TRUE)
p_faosoy <- full_path(p_fao, c("soybean_I", "soybean_R", "soybean_S"))
file.rename(faonms, full_path(p_fao, c("soybean_I", "soybean_R", "soybean_S")))
faonms <- dir(p_faosoy, full.names = TRUE)
renm <- paste0(p_faosoy, c("soybean_I", "soybean_R", "soybean_S"), ".tif")
file.rename(faonms[grep("res02_crav6190", faonms)], renm)

# load in tiffs, crop and mask to Zambia
faosoy <- lapply(renm, function(x) raster(x))
names(faosoy) <- c("soybean_I", "soybean_R", "soybean_S")
faosoy <- lapply(faosoy, function(x) {
  r <- crop(x, yld_rl$soybean$S)
  ro <- mask(r, yld_rl$soybean$S[[1]])
})
faosoy <- faosoy[names(faosoy)[3:1]]  # rearrange
plot(faosoy[[2]])

# dssat soy mean yield grids
dssatsoy_mu <- sapply(yld_rl$soybean, function(x) {
  r <- calc(x[[grep("ymu", names(x))]], mean)
})
sapply(dssatsoy_mu, function(x) cellStats(x, mean))

# Find mean yield differences
soydiff <- lapply(1:3, function(x) {
  faosoy[[x]] - dssatsoy_mu[[x]]
})
soydiffmsk <- lapply(soydiff, function(x) x < 0) # poss and negative

# Liuwa plains and wetland yields much higher than should be. Don't adjust

bias <- sapply(1:3, function(x) {
  r1 <- mask(soydiff[[x]], soydiffmsk[[x]] == 0, maskvalue = 0)
  r2 <- mask(soydiff[[x]], soydiffmsk[[x]] == 1, maskvalue = 0)
  c("mu1" = cellStats(r1, mean), "mu2" = cellStats(r2, mean), 
    "med1" =  quantile(r1, probs = 0.5), "med2" =  quantile(r2, probs = 0.5))
})

# calculate bias offset for different management types, filtering out wetland
# areas. Interpolate between rainfed subsistence and commercial because of 
# of overly high (3,500 kg/ha) rainfed high input bias
biasu <- bias[c(1, 3), ]
biasu[, 2] <- rowMeans(bias[c(1, 3), c(1, 3)]) # replace with interpolated
biasd <- bias[c(2, 4), ]  # down adjustment for wetlands
biasd[, 2] <- rowMeans(bias[c(2, 4), c(1, 3)]) # replace with interpolated

# median and mean bias about the same
# fix dssat yields, test first on just the mean yields
par(mfrow = c(2, 2))
soyadjtest <- lapply(1:3, function(x) {  # x = 1
  r1 <- (dssatsoy_mu[[x]] + biasu[2, x]) * (soydiffmsk[[x]] == 0)
  r2 <- (dssatsoy_mu[[x]]) * (soydiffmsk[[x]] == 1)
  r3 <- r1 + r2
  plot(r3)
})

# Fix all of them now
soyfix <- lapply(1:3, function(x) {
  ri <- yld_rl$soybean[[x]]
  r1 <- (ri + biasu[2, x]) * (soydiffmsk[[x]] == 0)
  r2 <- ri * (soydiffmsk[[x]] == 1)
  r3 <- r1 + r2
  names(r3) <- names(ri)
  r3
})
names(soyfix) <- names(yld_rl$soybean)
```

```{r, eval = FALSE}
yld_rl2 <- list(yld_rl$maize, soyfix)
names(yld_rl2) <- crops

for(i in 1:length(yld_rl2)) {
  rl <- yld_rl2[[i]]
  for(j in 1:length(rl)) {
    fnm <- full_path(p_yield, paste0(crops[i], "_", names(rl)[j], "_10K.tif"))
    writeRaster(rl[[j]], filename = fnm, overwrite = TRUE)
    layernms <- names(rl[[j]])
    save(layernms, file = gsub("\\.tif", "\\.rda", fnm))
  }
}
```
<a href="#top">Back to top</a>

@@

This provides the methods for taking 10 km grids, averaging them across cultivars within management treatments, and then resampling to 1 km grids. This is approximately the approach that will be used to make inputs for the tradeoff model. Other methods to explore include blending different types of management practice, e.g. X% of each cell is irrigated, Y% is rainfed commercial, Z% is subsistence. 
```{r, eval=FALSE}
yld_mus <- lapply(crops, function(x) {  # x <- crops[[1]]
  ymu <- lapply(c("S", "R", "I"), function(y) {  #y <- "S"
    cnms <- names(yld_rasts[[x]])[grep(paste0("mu_", y), names(yld_rasts[[x]]))]
    ylds <- copy(yld_rasts[[x]][, c("x", "y", cnms), with = FALSE])
    ylds[, c(x) := round(rowMeans(.SD)), .SDcols = cnms]
    ylds[, c(cnms) := NULL]
    ylds
  })
  named_out(ymu, c("S", "R", "I"))
})
names(yld_mus) <- crops
plot(dt_to_raster(yld_mus[[2]]$R, CRSobj = gcs))
